### 2018-02-09 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
2nd ODE P5 Notes

>>>>

\section{Substitution}
\setcounter{equation}{0}
\subsection{Example 1}
\textit{Show that the substitution $x=e^u$ transforms}
\begin{equation}\label{eq:1}
x^2\frac{d^2y}{dx^2}+x\frac{dy}{dx}+y=0
to
\begin{equation}\label{eq:2}
\frac{d^2y}{dx^2}+y=0
Find $\frac{dx}{du}$
$$\textrm{As} \ x=e^u, \ \frac{dx}{du}=e^u=x$$
Find $\frac{dy}{du}$ using the chain rule
\begin{equation}\label{eq:3}
\frac{dy}{du}=\frac{dy}{dx}\times\frac{dx}{du}=e^u\frac{dy}{dx}=x\frac{dy}{dx}
Find a simplification of $\frac{d^2y}{du^2}$
$$\frac{d^2y}{du^2}=\frac{d}{du}\Bigg(\frac{dy}{du}\Bigg)$$
Simplify using known expression for $\frac{dy}{du}$
$$\frac{d^2y}{dx^2}=\frac{d}{du}\Bigg(e^u\frac{dy}{dx}\Bigg)$$
Apply the product rule,using the chain rule to differentiate $\frac{dy}{dx}$ with respect to u
$$\frac{d^2y}{dx^2}=e^u\frac{dy}{dx}+e^u\frac{d^2y}{dx^2}\frac{dx}{du}$$
Replace $e^u\frac{dy}{dx}$ with $\frac{dy}{du}$ and $e^u$ and $\frac{dx}{du}$ each with x
$$\frac{d^2y}{dx^2}=\frac{dy}{du}+x^2\frac{d^2y}{dx^2}$$
Rearrange to find $x^2\frac{d^2y}{dx^2}$
\begin{equation}\label{eq:4}
x^2\frac{d^2y}{dx^2}=\frac{d^2y}{du^2}-\frac{dy}{du}
Substitute the results from \eqref{eq:3} and \eqref{eq:4} into \eqref{eq:1}.
$$\frac{d^2y}{dx^2}-\frac{dy}{du}+\frac{dy}{du}+y=0$$
Simplify to find answer
$$\frac{d^2y}{dx^2}+y=0$$
\textit{Solve this to find the general solution}
$$m^2+1=0$$
$$m=\pm i$$
Substitute into the general form
$$y=A\cos u+B\sin u$$
Substitute $u=\ln x$ to give GS in terms of x
$$y=A\cos(\ln(x))+B\sin(\ln(x))$$
